Inferring Continuous and Discrete Population Genetic Structure Across Space

### 2017-08-30 writeup/conStruct.tex
dropped sampling maps

Our data, originally published by \cite{Puckett2015}, consist of 95 individuals 
sampled across the United States and on the West coast of Canada,
genotyped at just under 22,000 bi-allelic loci (map of the sampling shown in Fig \ref{bear_map}).
The distribution of missing data across these individuals was uneven, 
with a few individuals representing most of the missing data, 
so we removed individuals with greater than 4\% missing data, 
resulting in a final dataset of 78 individuals.
We then analyzed these data, treating individuals as the unit of analysis, 
using both the spatial and nonspatial \texttt{conStruct} models with a $K$ of between 1 and 7, 
and compared these models using cross-validation.
The results of these analyses are shown in Figs \ref{bear_xvals} - \ref{bear_laycon}, 
as well as in Figs \ref{bear_sp_pies} - \ref{bear_nsp_clst_covs} in the Supplementary Materials.

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=4in]{figs/bears/bear_sampling_map.pdf}}
	\caption{
	Map of the sampled black bear individuals included in the analysis.
    }\label{bear_map}
\end{figure}

>>>>

Our data, originally published by \cite{Puckett2015}, consist of 95 individuals 
sampled across the United States and on the West coast of Canada,
genotyped at just under 22,000 bi-allelic loci.
The distribution of missing data across these individuals was uneven, 
with a few individuals representing most of the missing data, 
so we removed individuals with greater than 4\% missing data, 
resulting in a final dataset of 78 individuals.
We then analyzed these data, treating individuals as the unit of analysis, 
using both the spatial and nonspatial \texttt{conStruct} models with a $K$ of between 1 and 7, 
and compared these models using cross-validation.
The results of these analyses are shown in Figs \ref{bear_xvals} - \ref{bear_laycon}, 
as well as in Figs \ref{bear_sp_pies} - \ref{bear_nsp_clst_covs} in the Supplementary Materials.
